---
title: "Telcom Churn Random Forest"
---
```{r}
library(readr)
library(woe)
library(car)
require("randomForest")
require("ROCR")
#install.packages("neuralnet")
require(neuralnet)
#install.packages("nnet")
require(nnet)
require(ggplot2)
#install.packages("caret")
library(caret)
#install.packages("Metrics")
library(Metrics)
#install.packages("gbm")
library(gbm)
library(caTools)
#install.packages("e1071")
library(ROCR)
library(e1071)
library(caret)
library(dplyr)
#library(devtools)

#install.packages("woe")
library(woe)
#install.packages("devtools")
library(devtools)
#install.packages("riv")
library(riv) 

```


```{r}
churn <- read_csv("C:/Users/sandeep/Downloads/Predictive - Shung/Predicitive Dataset/WA_Fn-UseC_-Telco-Customer-Churn.csv")
attach(churn)
#str(churn)
```

## Add a new data column if output is categorical into numerical
```{r}
churn$churn_number <- 0
churn$churn_number[churn$Churn == 'Yes'] <- 1
#str(churn)
```

## Creating different bins for important variables and renaming them
##
```{r}
churn<-cbind(churn,class.ind(churn$InternetService))
names(churn)[names(churn)=="No"] <- "NoFibreOptic"
names(churn)[names(churn)=="DSL"] <- "Internet_DSL"
names(churn)[names(churn)=="Fiber optic"] <- "Internet_FiberOptic"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$OnlineSecurity))
names(churn)[names(churn)=="No"] <- "OnlineSecurity_No"
names(churn)[names(churn)=="Yes"] <- "OnlineSecurity_Yes"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$PhoneService))
names(churn)[names(churn)=="No"] <- "PhoneService_No"
names(churn)[names(churn)=="Yes"] <- "PhoneService_Yes"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$TechSupport))
names(churn)[names(churn)=="No"] <- "TechSupport_No"
names(churn)[names(churn)=="Yes"] <- "TechSupport_Yes"
names(churn)[names(churn)=="No internet service"] <- "TechSupport_No_Int"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$Contract))
names(churn)[names(churn)=="Month-to-month"] <- "Contract_MM"
names(churn)[names(churn)=="One year"] <- "Contract_OneYear"
names(churn)[names(churn)=="Two year"] <- "Contract_TwoYear"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$PaperlessBilling))
names(churn)[names(churn)=="No"] <- "PaperlessBilling_No"
names(churn)[names(churn)=="Yes"] <- "PaperlessBilling_Yes"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$Partner))
names(churn)[names(churn)=="No"] <- "Partner_No"
names(churn)[names(churn)=="Yes"] <- "Partner_Yes"
str(churn)
```

##
```{r}
churn<-cbind(churn,class.ind(churn$PaymentMethod))
names(churn)[names(churn)=="Electronic check"] <- "Electronic_check_PM"
names(churn)[names(churn)=="Bank_transfer_(automatic)"] <- "Bank_transfer"
names(churn)[names(churn)=="Credit_card_(automatic)"] <- "Credit_card"
names(churn)[names(churn)=="Mailed check"] <- "Mailed_check"
str(churn)
```
## Convert all characters into factors
```{r}
churn=churn %>% mutate_if(is.character, as.factor)
churn <- churn[,-1]
```

## Samlping
```{r}

sample = sample.split(churn$churn_number, SplitRatio = .75)
train_data = subset(churn, sample == TRUE)
test_data  = subset(churn, sample == FALSE)
nrow(train_data)
nrow(test_data)
str(train_data)
#train_data<- train_data[,-1]

```


## removed custimer_id (factor level was more than 7000) and Tech_Suport_NO_INT (was repeated twice)
```{r}
#taking ll predictor
str(train_data)
attach(train_data)
Churn.rf=randomForest(churn_number ~ gender + SeniorCitizen + Partner+Dependents+tenure+ PhoneService
                      +MultipleLines +InternetService +OnlineSecurity
                      +OnlineBackup+DeviceProtection+TechSupport
                      +StreamingTV+StreamingMovies
                      +Contract+PaperlessBilling
                      +PaymentMethod+MonthlyCharges+TotalCharges
                          , data = train_data )
Churn.rf
#plot(Churn.rf)

```

## try different random variables
```{r}
oob.err=double(19)
test.err=double(19)
#mtry is no of Variables randomly chosen at each split
for(mtry in 1:19) 
{
  rf=randomForest(churn_number ~ gender + SeniorCitizen + Partner+Dependents+tenure+ PhoneService
                      +MultipleLines +InternetService +OnlineSecurity
                      +OnlineBackup+DeviceProtection+TechSupport
                      +StreamingTV+StreamingMovies
                      +Contract+PaperlessBilling
                      +PaymentMethod+MonthlyCharges+TotalCharges
                          , data = train_data ,mtry=mtry,ntree=400)
   oob.err[mtry] = rf$mse[400] #Error of all Trees fitted
  
  pred<-predict(rf,test_data) #Predictions on Test Set for each Tree
  test.err[mtry]= with(test_data, mean( (churn_number - pred)^2)) #Mean Squared Test Error
  
  cat(mtry," ") #printing the output to the console
  
}
```

## Plot different error
```{r}
test.err
oob.err
matplot(1:mtry , cbind(oob.err,test.err), pch=19 , col=c("red","blue"),type="b",ylab="Mean Squared Error",xlab="Number of Predictors Considered at each Split")
legend("topright",legend=c("Out of Bag Error","Test Error"),pch=19, col=c("red","blue"))
```

## Test Data
```{r}
#str(test_data)
#test_data<- test_data[,-1]
str(train_data)
out_test <- predict(Churn.rf, test_data)
auc(test_data$churn_number,out_test)
out_train<- predict(Churn.rf,train_data)
auc(train_data$churn_number,out_train)

fit.results.churn_rf <- ifelse(out_test > 0.5,1,0)
misClasificError <- mean(fit.results.churn_rf != test_data$churn_number)
print(paste('Accuracy',1-misClasificError))

fit.results.churn_rf <- ifelse(out_train > 0.5,1,0)
misClasificError <- mean(fit.results.churn_rf != train_data$churn_number)
print(paste('Accuracy',1-misClasificError))
```

## Taking only important predictor
```{r}
Churn.rf_imp=randomForest(churn_number ~ tenure+ PhoneService
                      +InternetService +OnlineSecurity+TechSupport
                      +Contract+PaperlessBilling+PaymentMethod, data = train_data,ntree = 200, mtry = 2, importance = TRUE, proximity = TRUE )
Churn.rf_imp
fit.results.churn_rf <- ifelse(out_train_imp > 0.5,1,0)
misClasificError <- mean(fit.results.churn_rf != train_data$churn_number)
print(paste('Accuracy',1-misClasificError))

out_train_imp<- predict(Churn.rf_imp, train_data)
auc(train_data$churn_number,out_train_imp)
out_test_imp <- predict(Churn.rf_imp, test_data)
auc(test_data$churn_number,out_test_imp)
```

